Evaluación de impacto de la Reforma en Telecomunicaciones del 2013 en logro educativo en México

### 2021-05-11 final/pptx/presentacion.Rmd
Update presentacion.Rmd

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE, include=FALSE}
out = rdrobust(data$cambio_esp_top,data$cambio_internet, kernel = "triangular", c=15,p = 1, bwselect = "mserd",cluster=data$ClaveMun)
summary(out)
out1 = rdrobust(data$cambio_mat_top,data$cambio_internet, kernel = "triangular", c=15,p = 1, bwselect = "mserd",cluster=data$ClaveMun)
summary(out1)
```

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE,header=FALSE, include=FALSE}
out = rdrobust(data$cambio_esp_top,data$cambio_internet, kernel = "triangular", c=9,p = 1, bwselect = "mserd",cluster=data$ClaveMun)
summary(out)
out1 = rdrobust(data$cambio_mat_top,data$cambio_internet, kernel = "triangular", c=9,p = 1, bwselect = "mserd",cluster=data$ClaveMun)
summary(out1)
```
